Structural Divergence Analysis

### 2016-10-01 analysis-structure.Rmd
cambios 01-10-2016

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = 2, autodep = T)
```

@@

We use the Elastic Network Model with R0 = `r R0` for the `r family` family. 
We use as reference for the ENM the protein with pdb code `r reference`.
The `r family` family is of the type of `r type` and consists of the following proteins:

@@

print("agregar correlación")

@@

## experimental
exp.mean.z.RSD.vec <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file =  paste(p.ref, "_exp.pdb", sep = ""))

## mut
mut.mean.z.RSD.vec <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = paste(p.ref, "_mut.pdb", sep = ""))

## mut + sel / strong
strong.mean.z.RSD.vec <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = paste(p.ref, "_strong.pdb", sep = ""))
```

@@

```{r Pn-vs-mode-energy,cache = 2}
# plot Pn vs energy
dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

@@

```{r median-Pn-vs-mode-energy, cache = 2}
dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, autodep = T)
```

@@

We studied the `r family` family. 
We used the ENM `r enm` with R0 = `r R0` to generate mutants.
We used as reference for the ENM the protein with pdb code `r reference`. 
We simulated `r n.mut.p` mutants of this reference for each protein of the family.
The `r family` family is of the type `r type` and consists of the following proteins:

@@

print("agregar correlacion")

@@

## experimental
exp.mean.z.RSD.vec <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file =  file.path(data.dir, paste(p.ref, "_exp.pdb", sep = "")))

## mut
mut.mean.z.RSD.vec <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_mut.pdb", sep = "")))

## mut + sel / strong
strong.mean.z.RSD.vec <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_strong.pdb", sep = "")))
```

@@

```{r Pn-vs-mode-energy}
# plot Pn vs energy
dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

@@

```{r median-Pn-vs-mode-energy}
dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))
